The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-05-03 paper/ms.tex
Update acknowledgements

\acknowledgments
We would like to thank Megan Bedell, Robert A. Benjamin, Tobias Buck, Elena
D'Onghia, Benoit Famaey, and Adrian Price-Whelan for helpful discussions. A.B.
would like to thank Todd Phillips for helpful discussions. A.B. was supported
in part by the Roy \& Diana Vagelos Program in the Molecular Life Sciences and
the Roy \& Diana Vagelos Challenge Award. M.-M.M.L. was partly supported by
NSF grant AST18-15461. The work of D.A.-A., A.B., D.W.H., C.F.P.L., R.S.,
K.V.J., M.-M.M.L., and M.K.N. is supported by the Simons Foundation.

>>>>

\acknowledgments
We would like to thank Megan Bedell, Robert A. Benjamin, Tobias Buck, Elena
D'Onghia, Benoit Famaey, and Adrian Price-Whelan for helpful discussions. A.B.
would like to thank Todd Phillips for helpful discussions. A.B. was supported
in part by the Roy \& Diana Vagelos Program in the Molecular Life Sciences and
the Roy \& Diana Vagelos Challenge Award. K.V.J.'s work was performed in part
during the Gaia19 workshop and the 2019 Santa Barbara Gaia Sprint (also
supported by the Heising-Simons Foundation), both hosted by the Kavli
Institute for Theoretical Physics at the University of California, Santa
Barbara. K.V.J.'s contributions were supported in part by the National Science
Foundation under grants NSF PHY-1748958 and NSF AST-1614743. M.-M.M.L. was
partly supported by NSF grant AST18-15461. The work of D.A.-A., A.B., D.W.H.,
C.F.P.L., R.S., K.V.J., M.-M.M.L., and M.K.N. is supported by the Simons
Foundation.
